An Algorithm for Searching Evolving Graphs in Linear Algebraic Language

### 2016-01-22 paper.tex
update theorem 1

\begin{thm}[Correctness of evolving-graph BFS]
Let an evolving graph $G_n$ and a starting node $(s,t_0)$ be given.
The evolving-graph BFS discovers every active node that is reachable from the source $(s,t_0)$ and $dict.(v, t)$ is the length of the shortest temporal path
from $(s,t_0)$ to $(v,t)$.
\end{thm}
\proof
We could map an evolving graph $G_n$ to a static graph $G$ in such a way that
if there is an edge from $(v, t)$ to $(u,t)$ in $G_n$, there is an edge from $v_t$ to $u_t$ in $G$.
For any two nodes $v_s$ and $v_t$ in $G$,  if $s < t$, we add an edge from $v_s$ to $v_t$.
By construction, the forward-neighbors of an active node $(v, t)$ in $G_n$
are in one-to-one correspondence with the forward-neighbors of a node $v_t$ in $G$.
Hence the correctness of the evolving graph BFS follows from that of a static graph.
\endproof

\begin{thm}
 Algorithm \ref{alg:bfs} and Algorithm \ref{alg:bfsla} are equivalent.
\end{thm}
\proof
We shall check the two algorithms are equivalent in each module of
the method.
The initialization steps are trivially equivalent.
By the construction of $\bm{A^T}$,
step $9$ of Algorithm \ref{alg:bfsla} computes the forward-neighbors
of all the frontier nodes, which is equivalent to step $8$-$9$
of Algorithm \ref{alg:bfs}. Step $10$-$15$ of Algorithm \ref{alg:bfsla} ensures
active nodes will not be visited twice, which is equivalent to step $10$
of Algorithm \ref{alg:bfs}. Finally, a dictionary $dict$ is used in both algorithms
to keep record of the distance of each node from the source $(s,t)$.
\endproof

>>>>

\begin{thm}[Correctness of evolving-graph BFS]
Let an evolving graph $G_n$ and a starting node $(s,t_0)$ be given.
The evolving-graph BFS discovers every active node that is reachable from the source $(s,t_0)$ and $dict.(v, t)$ is the length of the shortest temporal path
from $(s,t_0)$ to $(v,t)$.
\end{thm}
\proof
We could map an evolving graph $G_n$ to a static graph $G$ in such a way that
if there is an edge from $(v, t)$ to $(u,t)$ in $G_n$, there is an edge from $v_t$ to $u_t$ in $G$.
For any two nodes $v_s$ and $v_t$ in $G$,  if $s < t$, we add an edge from $v_s$ to $v_t$.
By construction, an active node $(v,t)$ in $G_n$ is in one-to-one correspondence with
a node $v_t$ in $G$.
The forward-neighbors of an active node $(v, t)$ in $G_n$
are in one-to-one correspondence with the forward-neighbors of a node $v_t$ in $G$.
Hence the correctness of the evolving graph BFS follows from that of a static graph.
\endproof

\begin{thm}
 Algorithm \ref{alg:bfs} and Algorithm \ref{alg:bfsla} are equivalent.
\end{thm}
\proof
We shall check the two algorithms are equivalent in each module of
the method.
The initialization steps are trivially equivalent.
By the construction of $\bm{A^T}$,
step $9$ of Algorithm \ref{alg:bfsla} computes the forward-neighbors
of all the frontier nodes, which is equivalent to step $8$-$9$
of Algorithm \ref{alg:bfs}. Step $10$-$15$ of Algorithm \ref{alg:bfsla} ensures
active nodes will not be visited twice, which is equivalent to step $10$
of Algorithm \ref{alg:bfs}. Finally, a dictionary $dict$ is used by both algorithms
to keep record of the distance of each node from the source $(s,t)$.
\endproof
